Dutch, PPs, ʀ-pronouns

### 2019-12-19 paper.tex
werkt t?
vanaf de desktop
voor meeting with pavel

54586da0fa5bdbec34a4e83fcdf411ea6162a09a

@@

What this shows is that in principle \tit{waarmee} is used, it is the default. What is special about the examples in which \tit{met wat} is used then? I suggest that it is the constituency. \tit{Waarmee} needs to be a constituent. I repeated the \tit{waarmee} example. Here \tit{waar} and \tit{mee} are both part of the embedded clause. I show later that at some point in the derivation they were part of a proper constituent. They formed a constituent without any other elements.

@@

 Now I repeat the \tit{met wat} example. Here \tit{wat} is part of the embedded clause but \tit{met} is not. It belongs to the main clause. An embedded clause is finished before the main clause is built. At no point in the derivation can \tit{met} \tit{wat} form a proper constituent.

@@

@@

>>>>

@@

What this shows is that in principle \tit{waarmee} is used, it is the default. There is something special about the examples in which \tit{met wat} is used.

Now let us return to the mismatching headed relatives. The two predicates I used in these are \tit{kopen} `to buy' and \tit{schilderen}  `to paint'. \tit{Kopen} takes an accusative DP as its object. \tit{Schilderen} can take an instrumental PP as its object.\footnote{Of course, \tit{schilderen} also possibly takes an accusative DP, but I am focussing on the instrumental here.}

\ex.
\ag. Ik koop het schilderij.\\
 I buy the painting\\
 `I am buying the painting.'
\bg. Ik schilder met een kwast.\\
 I paint with a brush\\
 `I am painting with a brush.'

I repeat the example in which \tit{schildert} is in the embedded clause.

@@

\tit{Schildert} wants the instrumental PP, so the embedded clause looks like this:

\ex. [waar jij mee schildert]

Here \tit{waar} and \tit{mee} are both part of the embedded clause. At a certain point in the derivation they formed a proper constituent, i.e. they formed a constituent without any other elements.

\ex. \begin{forest} boom
[
    [waarmee]
    [schildert]
]
\end{forest}

\ex. \begin{forest} boom
[
    [jij]
    [
        [waarmee]
        [schildert]
    ]
]
\end{forest}

\ex. \begin{forest} boom
[
    [jij]
    [
        [
            [waar]
            [mee]
        ]
        [schildert]
    ]
]
\end{forest}

now move \tit{waar}

\ex. \begin{forest} boom
[
    [waar]
    [
        [jij]
        [
            [
                [mee]
            ]
            [schildert]
        ]
    ]
]
\end{forest}

or \tit{waarmee}

\ex. \begin{forest} boom
[
    [
        [waar]
        [mee]
    ]
    [
        [jij]
        [
            [schildert]
        ]
    ]
]
\end{forest}

Then in the main clause \tit{gekocht} is merged, which selects for an accusative object. Somehow \tit{waarmee} can satisfy that requirement.

Now I repeat the \tit{met wat} example.

@@

\tit{Schildert} wants the instrumental PP, so the embedded clause looks like this:

\ex. [waar jij mee schildert]

Here \tit{wat} is part of the embedded clause but \tit{met} is not. It belongs to the main clause. An embedded clause is finished before the main clause is built. At no point in the derivation can \tit{met} \tit{wat} form a proper constituent.

@@

How do I connect constituency and different spellouts of the instrumental? Nano: only constituents can spellout. Something interevened. More examples of that.

\section{internal structure of \tit{met wat} and \tit{waarmee}}

start with \tit{met wat}.

--here taking xxx apart--

--but first introduce a bit of theory--
